Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-07-28 document/ms.tex
Update formatting of aliases C15 and PHOENIX; for some reason they skip spaces sometimes.

\section{Methodology}\label{sec:methods}

\citet[hereafter \iancze]{czekala15} developed a modular framework\footnote{The open source codebase and its full revision history is available at \url{https://github.com/iancze/Starfish}.  The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.  The \iancze technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.  We employed the \PHOENIX~ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.  The modular framework was altered to accommodate starspot measurements in two ways. First, the single photospheric component was updated to includes a starspot spectrum. Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added in the starspot model.

@@

We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $m$.  We used the same analysis procedure as described for the ESPaDoNs spectra, with one exception.  For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.  No effort was made to shift the wavelength scales of the IGRINS data and $\PHOENIX$ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.

@@

\emph{Suitability of pre-computed \PHOENIX model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.  Cool sunspots are associated with heightened magnetic fields on the sun.  Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.  The former effect will differentially impact lines with high Lande-g factors (cite XX, fix the g formatting).  The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants (cite XX Saar and collaborators).  Our tacit assumption has been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures and 2) there exist many orders and lines that are not affected at all.  We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.  Strong metal lines demonstrate large departures in their best fit $\Z$ due to Zeeman broadening.  No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
% Note that these two effects would differently affect the spectra

@@

\iancze define a pixel-level forward model $\vM$ of the data.  A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.  The model encapsulates the major intrinsic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:

@@

The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.  We use the \PHOENIX model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.

@@

If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.  However \iancze employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:

>>>>

\subsection{Methodology}\label{sec:methods}

\citet[hereafter \iancze]{czekala15} developed a modular framework\footnote{The open source codebase and its full revision history is available at \url{https://github.com/iancze/Starfish}.  The experimental fork discussed in this paper is at \url{https://github.com/gully/Starfish}} to infer stellar properties from high resolution spectra.  The \iancze\ technique forward models ``emulated'' synthetic spectra from pre-computed model grids, taking into account the discretization error attributable to the coarsely sampled stellar intrinsic parameters.  We employed the \PHOENIX\ grid of pre-computed synthetic stellar spectra that span a wide range of wavelengths at high spectral resolution with sampling of 100 K in $\teff$ in our range of interest \citep{husser13}.  The modular framework was altered to accommodate starspot measurements in two ways. First, the single photospheric component was updated to includes a starspot spectrum. Second, the MCMC sampling strategy was altered to accommodate the additional free parameters added in the starspot model.

@@

We performed full-spectrum fitting on 32 of the 54 available IGRINS spectral orders, again fitting unique stellar parameters $\vt = (\teff, \logg, \Z)$ for each spectral order $m$.  We used the same analysis procedure as described for the ESPaDoNs spectra, with one exception.  For the IGRINS $K-$band, we employed an expanded search range for the effective temperature, $\teff \in [3000, 4200]$ K, since the IGRINS $H-$ band demonstrated some saturation at the $\teff=3500$ K lower bound.  No effort was made to shift the wavelength scales of the IGRINS data and \PHOENIX\ model into the same system, so the absolute values of $v_z$ are arbitrary shifted.

@@

\emph{Suitability of pre-computed \PHOENIX\ model spectra, model ranges, $\A \neq 0$, and magnetic fields-} We have assumed that the \PHOENIX\ synthetic spectra are a good representation to our observed IGRINS spectrum of \name, a young star likely to possess a large magnetic field.  Cool sunspots are associated with heightened magnetic fields on the sun.  Magnetic fields will have two effects on the emergent spectrum- line broadening attributable to the Zeeman effect, and pressure broadening attributable to seeing deeper into deeper layers in the photosphere compared to the surrounding hotter photosphere.  The former effect will differentially impact lines with high Lande-g factors (cite XX, fix the g formatting).  The latter effect could masquerade as an apparent shift in surface gravity, as seen in mixture models of spotted stars with empirical templates composed of dwarfs and giants (cite XX Saar and collaborators).  Our tacit assumption has been that these effects are 1) relatively small compared to the gross appearance and disappearance of spectral lines at disparate temperatures and 2) there exist many orders and lines that are not affected at all.  We see tentative evidence for physics outside of the pre-computed model grids in the poor fits to the observed spectra in $K-$band.  Strong metal lines demonstrate large departures in their best fit $\Z$ due to Zeeman broadening.  No pre-computed model grids including a range of surface magnetic fields are available at the wavelength range and spectral sampling needed to approach these questions within this spectral inference framework.
% Note that these two effects would differently affect the spectra

@@

\iancze\ define a pixel-level forward model $\vM$ of the data.  A flexible Gaussian Process noise model handles correlations in the residual spectrum, $\vR= \vD - \vM$.  The model encapsulates the major intrinsic stellar parameters $\vt_{\ast}$ and the extrinsic stellar parameters $\vt_{\rm ext}$:

@@

The $\vt_{\ast}$ are comprised of the dimensions of the pre-computed stellar model grid.  We use the \PHOENIX\ model grid \citep{husser13}, with fixed solar alpha abundances: $\A = 0$, so $\vt_{\ast} = \{\teff, \logg, \Z \}$.

@@

If the stellar models are in absolute flux units, our mixture model is complete as stated in Equation \ref{eqn:mix_M}.  However \iancze\ employ \emph{standardized} $\flam$ when constructing the forward model $\vM$:
